Package Tests

### 2020-08-15 r-package/tests_marcus/rjava_tests.Rmd

```{r}
trip
```

>>>>

 # input
 trip_date <- "2019-03-17"
 departure_time <- "14:00:00"
 street_time = 15L
 direct_modes <- c("WALK", "BICYCLE", "CAR")
 transit_modes <-"BUS"
 max_street_time = 30

trip_requests <- data.frame(id = 1:5,
                            fromLat = points[1:5,]$lat,
                            fromLon = points[1:5,]$lon,
                            toLat = points[96:100,]$lat,
                            toLon = points[96:100,]$lon )

trips <- multiple_detailed_itineraries( r5_core,
                                         trip_requests,
                                         trip_date = trip_date,
                                         departure_time = departure_time,
                                         direct_modes = direct_modes,
                                         transit_modes = transit_modes,
                                         max_street_time = max_street_time
                                         )
```

```{r}
 trips <- multiple_detailed_itineraries( r5_core,
                                         trip_requests,
                                         trip_date = trip_date,
                                         departure_time = departure_time,
                                         direct_modes = direct_modes,
                                         transit_modes = transit_modes,
                                         max_street_time = max_street_time
                                         )
```

```{r}
trips %>%
  ggplot() +
  geom_sf(aes(colour = mode)) +
  facet_grid(request~option)
```
